\documentclass[10pt, letterpaper]{article}
\usepackage[letterpaper, margin=0.5in]{geometry}
\usepackage{anyfontsize, tabularx, multirow, hyperref, titlesec, comment, enumitem}

% Font setting
%\usepackage{fontspec}
%\setmainfont[Ligatures=TeX]{Calibri}

\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{3pt}

\thispagestyle{empty}

% List style
\setlist[itemize]{leftmargin=*, before=\vspace{-0.5\baselineskip}, after=\vspace{-\baselineskip}, nosep}

% Customized multicolumn
\newcommand{\itemcols}[1]{
	\multicolumn{2}{p{\dimexpr \linewidth-2\tabcolsep}}{
	\begin{itemize}
		#1
	\end{itemize}
	}
}


\begin{document}
\noindent
\begin{tabularx}{\linewidth}{X r}
	\multirow{4}{*}{{\fontsize{45}{55}\selectfont Yue Wu}}
	& \href{mailto:yuw264@ucsd.edu}{yuw264@ucsd.edu} \\
	& (858) 666-5847 \\
	& \href{https://github.com/ALMSIVI}{https://github.com/ALMSIVI} \\
	& \href{https://www.linkedin.com/in/yue-wu-aaab2213b/}{https://www.linkedin.com/in/yue-wu-aaab2213b/}
\end{tabularx}

% If explicitly asked to, uncomment.
%\begin{comment}
\noindent
\textbf{Looking for full-time Software Engineer opportunities starting Summer 2020.}
%\end{comment}

% Header including mailing address
\begin{comment}
\begin{tabularx}{\linewidth}{X r}
\multirow{4}{*}{{\fontsize{45}{60}\selectfont Yue Wu}} 
& \href{mailto:yuw264@ucsd.edu}{yuw264@ucsd.edu} \\
& (858) 666-5847 \\
& 8840 Costa Verde Blvd. Apt. 3322 \\
& San Diego, CA 92122
\end{tabularx}
\end{comment}


\section{Education}
\smallskip
\noindent
\begin{tabularx}{\linewidth}{X r}
	\textbf{\large University of California, San Diego} & \texttt{09/2016-06/2020} \\
	\itemcols{
		\item B.S. in Computer Science, Minor in Visual Arts: Computing and Arts \textbf{(Cumulative GPA: 3.917/4)}
		\item Courses Taken: Data Structures, Algorithms, Software Engineering, HCI Design, Computer Graphics, Operating Systems, Programming Languages, Compilers, Deep Learning
	}
\end{tabularx}


\section{Skills}
\smallskip
\noindent
\begin{tabularx}{\linewidth}{l X}
	\texttt{Language} & C\#, Java, Javascript/Typescript, C, C++, Python, Haskell, \LaTeX, Shader (GLSL, HLSL/ShaderLab) \\
	\texttt{Framework} & Unity, SteamVR, WPF, Android, jQuery, Node.js, SQL, OpenGL/WebGL, React.js. THREE.js \\
	\texttt{Software} & Visual Studio, Android Studio, vim, Blender, git, Linux
\end{tabularx}


\section{Work Experience}
\smallskip
\noindent
\begin{tabularx}{\textwidth}{X r}
	\textbf{\large Intern Data Visualization Engineer}, Alibaba Inc., Hangzhou, China & \texttt{06/2019-08/2019} \\
	\itemcols{
		\item Constructed a backend graph layout library for 3D graph visualization using Typescript, where I integrated force-directed layout and Sugiyama algorithm, the library is more flexible than d3.js.
		\item Developed a geographic model generation service featuring a Marching Square algorithm 100x more precise and more powerful than turf.js, that will be used in press conferences, including the Double 11 Festival.
		\item Collaborated with a naked eye 3D project team to discover data visualization and HCI in Unity/WebGL, where I explored Entitas, a data-oriented framework similar to Redux, and wrote shaders for various effects.
	} \\

	\textbf{\large Unity Developer}, UCSD Qualcomm Institute, La Jolla, California & \texttt{10/2018-06/2019} \\
	\itemcols{		
		\item Built an iOS AR app for PricewaterhouseCoopers (PwC)'s Bodylogical software.
		\item Designed three visualization modules in Unity (ARKit) that would allow data to be presented in 3D space across different time frames, allowing the user to easily grasp the core functions of the simulator.
		\item Implemented an XML-based localization system and a tutorial system from scratch so that PwC can demonstrate the app to non English speakers who might be new to AR.
	} \\

	\textbf{\large Intern Full Stack Developer}, LMT Technology, Shanghai, China & \texttt{06/2018-08/2018} \\
	\itemcols{
		\item Refactored company's product from Flash to HTML/Javascript, and from a custom backend to Spring, reducing code length and boosting execution efficiency.
		\item Poinpointed and addressed localization and responsive UI issues, making the product more foreigner-friendly and improving user experience.
		\item Introduced JSDoc, a documentation format for Javascript, to the team, setting up a uniform code format.
	}
\end{tabularx}


\section{Selected Projects}
\smallskip
\noindent
\begin{tabularx}{\linewidth}{X r}
	\textbf{\large MechSuit VR}, Unity Developer & \texttt{04/2017-06/2019} \\
	\itemcols{
		\item Joined the school's Virtual Reality Club to work on a Unity fighting game featuring Steam VR (Vive).
		\item Implemented the inverse kinematic system for the armor using the positions of the VR headset and hand-held controllers, which boosted player control efficiency.
		\item Programmed a propulsion system with player movements as input, enabling motion control for players, who would physically move to traverse through the arena instead of using the joystick.
		\item Designed health and weapon systems, and UI for health and ammo display using MVC, writing scripts with Strategy Pattern so that they can be easily extended for various damage types and player resistances.
	} \\
	
	\textbf{\large Transracer}, Full Stack Developer & \texttt{04/2018-06/2018} \\
	\itemcols{
		\item Worked in a 4-person team to create a web application with both front end (Bootstrap) and back end (Node.js) that allows user to learn different languages through translating lyrics.
		\item Developed all the database logic with sqlite for songs and scores, so that users can upload their favorite songs to the app for practice, and view their past attempts.
		\item Improved score calculation based on the number of hints the user relies on and the correctness of the answer.
	} \\
	
	\textbf{\large Flashback Music}, Android Developer & \texttt{01/2018-03/2018} \\
	\itemcols{
		\item Worked in a 5-person, Agile team to create an Android music application that records the time and location songs are played so that users could reminisce on their moods.
		\item Separated UI interaction and back end logic with Model-View-Controller pattern resulting in cleaner code.
		\item Devised separate logic for local and cloud music under a set of interfaces with Strategy and Factory patterns.
	}
\end{tabularx}

\begin{comment}
\textbf{\large WayAround}, Front End Developer & \texttt{01/2018-03/2018} \\
\itemcols{
\item Worked in a 4-person team to create a web application mockup. The app allows users to customize their routes so as to enjoy the trip to the destination.
\item After paper prototypes, implemented the home page with Bootstrap, jQuery and Handlebars.js, where the users would customize the route. Wrote two versions of the page for A/B testing, analyzing the time each user used in navigating through the page to find out how users would approach a new product and modified to make the page user-friendly.
\item Perfected the review page, where the user rates the route based on their customization back on the home page.	
} \\
\end{comment}

% Not a big deal
\begin{comment}
\section{Awards}
\smallskip
\noindent
\begin{tabularx}{\linewidth}{X r}
	10th place at UCSD WIC Beginner's Programming Competition & \texttt{06/2017}
\end{tabularx}
\end{comment}

% Not useful for job seeking
\begin{comment}
\section{Interests}
\smallskip
\noindent
I am fascinated by popular art (comics, games as well as rock music) and always wonder how far computers can take me in creating art. This leads me to minor in Visual Arts.
\end{comment}
\end{document}